\thesistitle

### 2019-07-17 sections/clonerefactor.tex
Create equality array

\subsubsection{CloneRefactor method of removing redundant clone classes}

@@

>>>>

\subsubsection{CloneRefactor method of removing redundant clone classes}
Because of the order in which clones are found in the clone graph, removing redundant clone classes can be optimized to not require a search of the entire set of clones. To do this, we mark each node that has been considered for duplication as \textit{visited}. This includes nodes that are interated over and all duplicates of those nodes. When we later find a new clone class of which all nodes are \textit{visited}, we don't add this clone class to the set of clone classes because it is a subset of an existing clone class.

\todo{Removal of existing clones: How does this is possibly redundant thing work?}

@@

\subsubsection{Create equality array}
To determine the difference in literals, method calls and variables, we convert the code to an equality array. This equality array converts each (group of) token(s) to a number unique to that (group of) tokens. Each literal, method call or variable becomes a positive number, whereas each other token becomes a negative number. An example of two code fragments converted to equality arrays is displayed in figure \ref{fig:equalityarrays}.

\begin{figure}[H]
  \centering
  \includegraphics[width=1\columnwidth]{img/equality}
  \caption{The conversion of code to an equality array.}
  \label{fig:equalityarrays}
\end{figure}
